% * Preamble
\documentclass{article}
% ** Packages
\usepackage[latin9]{inputenc}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 1},backref=section,colorlinks=false]
 {hyperref}
\hypersetup{
 colorlinks,citecolor=black,filecolor=black,linkcolor=red,urlcolor=black,linktocpage}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.

\usepackage{fullpage}
% ** Title and date
\title{Chicago Men's A Cappella Bylaws}
\date{May 27, 2014}



\makeatother


\begin{document}
\maketitle

% * Changelog
\noindent \textbf{Changelog:} \\
 %
\begin{tabular}{l}
Amended and updated May 25, 2014
Ratified May 23, 2013. \tabularnewline
Amended and updated May 18, 2013. \tabularnewline
Amended April 18, 2013. \tabularnewline
Ratified May 15, 2012. \tabularnewline
Amended and updated May 5, 2012. \tabularnewline
Ratified May 19, 2011. \tabularnewline
Amended and updated April 15, 2011. \tabularnewline
Ratified April 27, 2010. \tabularnewline
Amended and updated April 25, 2010. \tabularnewline
Ratified June 1, 2009. \tabularnewline
Amended and updated April 14, 2009. \tabularnewline
Ratified November 2007. \tabularnewline
Amended and updated October 9, 2007. \tabularnewline
Ratified May 10, 2007. \tabularnewline
\end{tabular}

% * Table of contents
\noindent \newpage{}

\tableofcontents{}

% * Name
\newpage{}
\section{Name}
\begin{enumerate}
\item The name of the group shall be CMAC: The University of Chicago Glee Club.
\item The name shall be changed by motion and second from the floor at the
Annual Meeting, followed by a three-fourths vote in the affirmative
and majority approval of the Board.
\end{enumerate}

% * Mission
\section{Mission}

CMAC exists first and foremost to foster the growth and development
of its members both musically and personally. CMAC also strives to
maintain the highest musical quality as an ensemble and to enrich
both the Hyde Park and University of Chicago communities.

% * Membership
\section{Membership} \label{membership}

% ** Definition
\subsection{Definition}

Members:
\begin{enumerate}
  \item have been recommended by the Conductor for Membership; and
  \item have been approved and invited by the Board; and
  \item have accepted the invitation of Membership.
\end{enumerate}
Members who are registered students of the University of Chicago have voting
privileges for meetings of the Membership and Annual Meetings, except where
otherwise specified.  In abiding by Office of the Reynolds Club and Student
Activities rules, Members who are not registered students of the University of
Chicago will have no voting privileges.

The Board shall decide whether or not to invite a Recommendee who is a student
of the University of Chicago by majority vote. In the case where the Recommendee
is not a student of the University of Chicago, the decision to invite shall only
be made by unanimous vote of the Board.

% ** Section
\subsection{Section}

The Conductor shall assign each Member to one of four sections which
correspond to the four musical voice parts for men's voices and to
any sub-sections or additional sections as necessary.

% ** Period of Membership and Dues
\subsection{Period of Membership and Dues}

Excepting resignation or removal from Membership pursuant hereto,
each Member shall retain his Membership for so long as he shall remain
a student at the University of Chicago (or, in the case of a non-student,
for one year following his entrance into Membership) and continue
to pay such dues as may be determined under these Bylaws.

% ** Alumni
After three consecutive quarters of membership (or two, if the member's first
quarter was Winter quarter), the member is eligible to become a CMAC Alum
(hereafter simply Alum) when they surrender their Membership have graduated from
the University.

% ** Member Attendance
\subsection{Member Attendance} \label{attendance}
\begin{enumerate}
\item Members shall make every attempt to attend all regular rehearsals,
  meetings, and performances (as defined in Section 5.1).
\item Members who agree to perform in a gig (as defined in Section 5.5) shall
  make all attempts to attend it.
\item Members shall make every attempt to attend special rehearsals, sectionals,
  and meetings (as defined in Section 5.2)
\item A Member who does not attend any rehearsal or performance shall be
  considered absent from that rehearsal or performance.
\item Arrival of a Member to a regular rehearsal or performance after the
  scheduled start time shall be considered a tardy. Two tardies shall equate to
  an absence.
\item Absence of a Member from a regular rehearsal or performance for twenty
  minutes or more shall be considered absent.
\item Prior to an absence or tardy, Members must notify the entire executive
  board of their upcoming absence/tardy via email, providing their reason.
\item Unless excused in advance by the Board, attendance at all Dress Rehearsals
  is mandatory for performance in a concert.
\item A Member who has accrued three absences during one regular academic
  quarter shall be required to have a meeting with the Officers within one week
  of the third absence for review. Officers shall review the Member's
  performance, attendance and prior notifications of absences and decide what
  action to take by a majority of the Board. Decisions shall be made attempting
  in all cases to preserve both the musical and ethical integrity of the group.
\item A member who has accrued three or more absences in one academic quarter
  shall be considered to have excessive absence and faces disciplinary action,
  potentially exclusion from an upcoming performance.
\item Under extenuating circumstances, the above clauses may be lifted on
  an individual basis by a majority vote of the Officers.
\end{enumerate}

% ** Probation
\subsection{Probation}

The Executive Officers of the group may vote by majority whether to
put a Member on probation if:
\begin{enumerate}
\item Said Member is absent three or more times within a quarter; or
\item The Conductor recommends probation for said member; or
\item Said Member fails to attend performance.
\end{enumerate}
The limit and terms of said probation period shall be determined by
the Board and the Conductor but may include the prohibition
of said member from rehearsals, gigs, and/or performances. If the
member in question violates the terms of the probation period the
Board may then begin proceedings to remove said members from the group.

% ** Lapse of Membership
\subsection{Lapse of Membership}
\begin{enumerate}
\item A Membership lapses when a Member takes an extended break from
  participation in CMAC. This Member may be said to be ``on break.''
\item Conditions for lapsing are:
  \begin{enumerate}
  \item The Member communicates to exec in writing that they wish to take a
    break, or that they plan to miss 6 consecutive rehearsals.
  \item Any Member who is absent from 6 consecutive rehearsals is automatically
    considered to be on a break.
  \end{enumerate}
\item Members on break forfeit all voting privileges.
\item If the Member does not return to full participation (as determined by the
  Board) in the quarter following their first full quarter on break, then the
  Member automatically forfeits their Membership, but without forfeiting their
  ability to become an Alum. The Board may grant only a single quarter extension
  on a case-by-case basis.
\item The only exception to the preceding rule is in the case that a Member is
  gone from the University for a maximum of three academic quarters
  (e.g. studying abroad). In this case, the lapse may last for that single
  academic year, with no extension.
\item A Member may return from break to full membership in the first week of
  Fall or Winter quarter, without needing Board approval. A Member may only
  return from break otherwise with a unanimous vote of the full Board, and the
  Board having consulted with the Conductor. In the case where the Board forbids
  a Spring quarter return, the Board may grant a single quarter extension of
  lapse even when it would be otherwise disallowed by these rules.
\end{enumerate}

% ** Removal from Membership
\subsection{Removal from Membership}
\begin{enumerate}
\item Membership may be rescinded under the following conditions:

\begin{enumerate}
\item Uncontrollable tardiness or absenteeism; or
\item Egregiously inappropriate behavior, whether within CMAC or within the
  larger community; or
\item Violation of terms of probation; or
\item Any other behavior which the Board finds to be sufficiently serious and
  detrimental to the group.
\end{enumerate}
\item The following procedure shall be followed regarding the removal of
members from CMAC:

\begin{enumerate}
\item At a Meeting of the Board, one Officer shall first state the reasons
for removal and then shall make a motion to recommend to the Members
that said member (the Accused) shall be removed. A second for the
motion is required.
\item The Board shall then vote on the motion for removal from membership.
A simple majority is required for passage of the motion.
\item If the motion passes, then the Board shall:

\begin{enumerate}
\item immediately inform the Accused in writing of the decision and of
the reasons for the said decision; and
\item at the next regularly scheduled rehearsal, call an emergency meeting
of the Members to discuss and to vote on the removal of the Accused
from membership.
\end{enumerate}
\item The following shall occur at the Emergency Meeting:

\begin{enumerate}
\item The Board shall give their rationale for the recommendation to
remove the Accused from membership.
\item The Accused or the Accused's representative shall then give a defense
of the Accused and shall respond to the rationale given by the Officers.
\item Speaking times for the Board and for the Accused or their representative
shall be equal.
\item The President shall then open the floor to all members (including the
  Accused) who wish to discuss the recommendation to remove the Accused. Every
  member who wishes to speak shall be given the opportunity to do so. The
  President shall announce proceedure for the following discussion, including at
  a minimum that none shall speak out of turn and that none shall speak but when
  the President gives them the floor. These rules shall be strictly enforced,
  and multiple violations or egregious violation shall result in expulsion from
  the discussion space and forfeiture of speaking rights within the discussion.
\item When no one else wishes to speak, the Accused shall leave the room
and a Member shall then move to remove the Accused from membership.
A second is required.
\item The Members shall then vote to remove the Accused from membership.
The motion carries if two thirds of those assembled support the motion.
\end{enumerate}
\end{enumerate}
\item Any member removed by the proceedure described in this section is no
  longer eligible to be an Alum.
\end{enumerate}

% * Rehearsals and Performance
\section{Rehearsals and Performance}

% ** Regular Rehearsals
\subsection{Regular Rehearsals}

During each regular academic quarter, Regular Rehearsals shall be held twice
weekly at such times and locations as to be designated by the Board and
Conductor. The day and time of Regular Rehearsals shall be announced to the
Members no later than the Sunday preceding the beginning of the regular academic
quarter. Regular Rehearsals shall be held during all weeks of the quarter except
for Finals Week.

% ** Special Rehearsals
\subsection{Special Rehearsals}

Special Rehearsals are all scheduled rehearsals other than those at the Regular
Rehearsal day and time. Special Rehearsals shall be held at such times and
locations as may be designated by the Board, Section Leaders (\ref{section_leaders}),
and the Conductor. The Board, Section Leaders, and the Conductor shall make
every effort to announce the Special Rehearsal to membership as far in advance
as possible.

% *** Sectional
A Sectional is a Special Rehearsal held for a single Section. Each Section shall
have two Sectionals per quarter, one to be held before the beginning of 5\textsuperscript{th}
week, and one to be held before the beginning of 9\textsuperscript{th} week.

% *** Retreat
A Retreat is an overnight trip including a long Special Rehearsal. The Board
shall make every effort to schedule a Retreat during the first four weeks of
Fall Quarter.

% ** Extension of Rehearsals
\subsection{Extension of Rehearsals}

The Conductor may extend the duration of any Rehearsal by not more
than fifteen minutes without prior notice, but any Member, with notification
and consent of the President, shall be able to leave at the regular
rehearsal time.

% ** Performances
\subsection{Performances}

All performances scheduled for the current academic quarter shall
be announced to the membership at the first regular meeting held after
they are scheduled during said quarter.

% *** End-of-Quarter Concert
The Group shall perform a concert on the weekend following tenth week of each
regular academic quarter. This concert is referred to as the End-of-Quarter Concert.

% *** Gigs
\subsection{Gigs}

A gig shall be defined as any CMAC performance that is not the End-of-Quarter
Concert. A gig shall be scheduled as follows: upon motion of the Board, the
President shall call for volunteers from the Members for a proposed gig. If the
Conductor determines that the number and voice parts of any volunteers are
appropriate for the gig, the same shall be scheduled.

% * Meetings of Membership
\section{Meetings of Membership}

% ** Annual Meeting
\subsection{Annual Meeting}

The Executive Board shall hold one meeting of all members before the sixth week
of Spring Quarter in order to deal with group business as needed and in order to
elect a new Board. The meeting shall be announced to the Membership at large no
less than two regular rehearsals immediately preceding the Annual
Meeting.

% ** Special Meetings
\subsection{Special Meetings}

Special Meetings of the members may be called by the President, the Board, or by
petition signed by one-third of the Membership. In the first case, the President
chairs the meeting. In the second case, the Board elects the Chair by majority
vote. In the third case, the petition must specify a Chair. Except in cases of
emergency, the Special Meetings shall be announced no less than two consecutive
regular rehearsals immediately preceding the Meeting. These meetings shall be
called to order for business that requires the considerations of the members.

% ** Quorum
\subsection{Quorum}

Unless otherwise provided by these Bylaws, at any meeting of the Members,
a majority of the Members shall constitute a quorum. At any election
meeting, including the Annual Meeting, two-thirds of the Members shall
constitute a quorum.

% ** Meeting Chair
\subsection{Meeting Chair}

All business meetings of the Members shall be chaired by the President,
or as designated by these Bylaws. The Chair may appoint a member to
record votes, or as otherwise needed to assist him.

% * Executive Board
\section{Executive Board} \label{board}
% ** Executive Board
\subsection{Executive Board}

The Executive Board (hereafter ``the Board'') shall be composed of the Executive
Officers (hereafter ``Officers'') of President, Treasurer, Publicity Chair,
Development Chair, and Secretary. The Board shall be elected at the Annual
Meeting and shall assume office as designated by these Bylaws. The qBoard shall
be responsible for the management of all CMAC activities, funds, and day-to-day
operations, and shall have all agency of CMAC necessary to carry out these
responsibilities. Each Officer shall be granted one vote on the Board.

All Officer-candidates shall:
\begin{enumerate}
\item Be students of the University of Chicago in good standing;
and
\item Have been Active Members for two of the previous three quarters, including
the current quarter, or in special circumstances, have been approved
by the Membership for candidacy; and
\item If elected, serve for no more than two consecutive years in the same
position; and
\item Plan to be in Chicago for at least two quarters of the academic year
in which they serve; and
\item Inform the Membership during elections of any prolonged absences.
\end{enumerate}

% ** Duties of the Board
\subsection{Duties of the Board}

The Board is responsible for the general administration of the group
and allotment of any and all CMAC monies. No later than the third
rehearsal of every quarter the Board shall publish the requirements
and responsibilities of every member. This document shall include,
but is not limited to, concert dates and times, rehearsal dates and
times, gig dates and times, and any other membership obligations.
The Board shall have sole discretion over invitations to Membership
and oversee any disciplinary action. The Board shall fix dates and
times for all concerts during the academic year as soon as possible.
Upon election of incoming Officers, the outgoing officers are responsible
for training of incoming Officers. Additionally, at the end of their
tenure each officer must prepare a written report of their actions
and thoughts during their tenure.

% ** Description of Offices
\subsection{Description of Offices}

% *** Delegation of Responsibility
\subsubsection{Delegation of Responsibility}

An officer is personally responsible for completing the duties assigned
to him in these Bylaws.

% *** President
\subsubsection{President}

The President is the chairman of the Executive Board; as such he sets agendas
for meetings. Additionally, he shall oversee the execution of all executive
duties. He is ambassador to both the University and the Community. He is
responsible for storage and maintenance of all CMAC property, except where
otherwise noted. In addition the President is responsible for keeping CMAC in
compliance with all applicable laws and regulations.

% *** Treasurer
\subsubsection{Treasurer}

The Treasurer shall be responsible for supervision of all financial
accounts; the collection, banking, and dispersion of all CMAC monies
as deemed appropriate by the Board. He is the signator of all CMAC
accounts. The Treasurer may not, under any circumstance, approve any
transaction without the Board's consent. These responsibilities shall
include, but be not limited to, the planning and implementation of
an annual budget, accurate bookkeeping of all CMAC accounts, and applying
for funds. In the Treasurer's quarterly report to membership and alumni,
he should give a financial synopsis including transactions and current
balances.

% *** Publicity Chair
\subsubsection{Publicity Chair}

The Publicity Chair is responsible for recruitment activities and shall also be
responsible for special invitations, concert posters, and concert
advertisement. The Publicity Chair is responsible for all CMAC advertising and
the storage and maintenance of all CMAC advertising materials.

% *** Development Chair
\subsubsection{Development Chair}

The Development Chair shall pursue opportunities related to the internal
and external development of the group including, but not limited to:
soliciting donations, seeking sponsorships, coordinating Alumni donations, and
creating merchandising opportunities. As such, the Development Chair is
responsible for storage and maintenance of CDs. The Development
Chair shall be responsible for the distribution of newsletters to
parents, alumni, and donors.

% *** Secretary
\subsubsection{Secretary}

The Secretary must record Board meeting minutes, and communicate them to CMAC at
large. Additionally, the Secretary is responsible for maintaining accurate
attendance records, and reporting to the Board any truancy worthy of
disciplinary action. The Secretary is responsible for the maintenance of all
CMAC contacts, including but not limited to university administrators, alumni,
and gig contacts.

% ** Meeting of the Officers
\subsection{Meeting of the Officers}

The Officers shall meet immediately following one rehearsal of every
week. At this meeting each officer should give his weekly report.
Furthermore, the Officers shall listen to any petitions brought to
it under Section 4 at this time. Additional meetings may be called
to address immediate or emergency issues. Minutes will be recorded
and disseminated by the Secretary. Any member of the group may attend
this meeting.

% ** Election of Officers
\subsection{Election of Officers} \label{elections}

% *** Election Meeting
\subsubsection{Election Meeting}

At the Annual Meeting of the members, as designated by Section
\ref{annual_meeting} of these Bylaws, the Members shall hold elections for the
offices of President, Treasurer, Publicity Chair, Development Chair, and
Secretary. The meeting shall be chaired by the current President or as
designated by these Bylaws, and a non-candidate member shall be appointed by the
Executive Board for the recording of votes. A quorum shall be two-thirds of the
current membership.

% *** Nomination of Candidates
\subsubsection{Nomination of Candidates}

Candidates for office shall be nominated and seconded by any two Members.
Upon acceptance of nomination, all candidates shall be given the opportunity
to address the membership for a period of time decided by a majority
of the electoral body prior to balloting for each office. Members
wishing to serve who have not been nominated may request nomination
from the Chair, in which case the Chair shall open the floor for nominating
the Member who has expressed interest in running.

% *** Discussion of Qualifications
\subsubsection{Discussion of Qualifications}

Following address by all candidates, the candidates shall leave the meeting and
non-candidate members shall be given an opportunity to discuss qualifications of
candidates for a period of time decided by a majority of the electoral body
prior to balloting for each office. Time of discussion may be extended as
needed, as shall be decided by a majority vote made from a motion on the
floor. The Chair may choose to extend the time by his discretion if he deems it
necessary. This discussion is sealed.

% *** Election by Majority
\subsubsection{Election by Majority}

Executive Officers shall be elected by a majority vote of a quorum
of the membership, as designated by these Bylaws, and each member
shall have one vote. If a majority vote of a quorum is not reached
on the first vote, the candidate receiving the lowest number of votes
will be removed from the ballot and the process shall be repeated
until a majority is reached. If a majority vote between two candidates
cannot be reached, the chair may call for another vote or call for
further discussion. All votes shall be done by secret ballot and shall
continue until each office is filled.

% *** Order of Elections
\subsubsection{Order of Elections}

The order of elections shall be President, Treasurer, Development
Chair, Publicity Chair, and Secretary. Provided his eligibility and nomination,
a non-elected member may run for more than one office, but if he is
elected to one, he shall immediately drop all candidacy for other
offices. No member shall serve in more than one position on the Executive
Board.
% *** Officers-Elect
\subsubsection{Officers-Elect}
Following election, all Officers-Elect are expected to attend all Board meetings
for the remainder of the quarter. The Officers-Elect hold no vote in these
meetings, but are expected to learn from the incumbent Board. Officers-elect
become Officers with voting privileges and responsibilities after the end of
Spring quarter.

% ** Impeachment of Officers
\subsection{Removal of Officers}

In the case of flagrant incompetence, the Members of CMAC shall, by a
three-fourths vote (two-thirds of Members being a quorum) choose to impeach any
Officer of the Board. The accused officer shall be given no less than two
minutes to make a case for his retainer, which shall immediately be followed by
a vote. A three-fourths vote of the quorum (not including the accused officer)
shall be required for removal. For simple incompetence, the former Officer shall
face no further punishment. If the incompetence extended to behavior
unacceptable for any Member, then further remedies may be proposed, as outlined
in previous sections.

% ** Succession
\subsection{Succession}

% *** President
\subsubsection{President}

In cases of temporary absence not lasting for more than one academic
quarter, the Treasurer shall serve as Acting President, and the Executive
Board shall, within one month of the beginning of the absence, vote
to appoint an Acting President for the duration of the absence. Such
an appointment shall be effective unless objected to, either verbally
or in writing, by one third of the voting members of the group, at
which time a special election for the position of Acting President
shall be called by the Treasurer. If the Executive Board, or possibly
the aforementioned special election, selects a current member of the
Executive Board, the fifth vote on the board will be granted to a
member of the group as defined below in \ref{temporary_voting}.

% *** All Other Officers
\subsubsection{All Other Officers}

In the case of impeachment or any other inability to serve for the remainder of
the year among the remainder of the Executive Board, the President shall
immediately hold a special election for the general membership to elect a
replacement officer by a majority vote, following the rules and regulations set
forth by Section \ref{elections}. In cases of temporary absence not lasting for more than
one academic quarter, the President shall call a special meeting in which an
acting officer shall be elected for the duration of the absence.

% *** Temporary Executive Voting Privileges
\subsubsection{Temporary Executive Voting Priviledges} \label{temporary_voting}

If the Executive Board should find itself with four or fewer Officers
with Executive Voting rights, the Membership may grant Executive Voting
privileges to one of the Members by majority vote. No other Executive
privileges or duties will be granted to this Member. The Member shall
hold temporary Executive Voting privileges until there exist a full
Board with Executive Voting privileges.

% * Executive Cabinet
\section{Executive Cabinet}

The Executive Board may appoint Executive Cabinet members at its discretion
to administer the operational duties of the Executive Board. The Cabinet
may include the positions of Stage Manager, Special Event Chair,
Social Chair, Philanthropy Chair, Music Chair, Newsletter Chair, Webmaster,
and Librarian. Additional Executive Cabinet positions may be appointed
by the Executive Officers as they deem fit. Cabinet members shall
have no vote on the Executive Board. \\
 All Executive Cabinet Appointees shall:
\begin{enumerate}
\item be students of the University of Chicago in good standing;
\item if appointed, serve for no more than two consecutive years in the
same position;
\item be in Chicago for at least two quarters of the academic year for which
they are appointed; and
\item inform the Executive Board of any conflicts and prolonged absences
during the academic year for which they are appointed.
\end{enumerate}

% ** The Duties of the Executive Cabinet
\subsection{The Duties of the Executive Cabinet}

All Cabinet members shall complete all tasks assigned to their position
by the Executive Board and enumerated herein. Cabinet members will
be summoned to attend two Executive Board meetings per quarter, unless
instructed otherwise by the Executive Board, and are encouraged to
attend all Executive Board meetings.

% ** Description of Positions
\subsection{Description of Positions}


\subsubsection{Stage Manager}

The Stage Manager shall be responsible for the logistics of the quarterly
concert. His specific duties shall include, but not be limited to,
coordinating ushers, compiling programs, and preparing performance
and rehearsal space. He will be required to attend all Executive Board
meetings as requested. He shall report to the President.


\subsubsection{Ticket Czar}

The Ticket Czar shall be responsible for printing, distributing, and
tracking tickets for quarterly performances. He shall also be responsible
for collecting ticket money from all the members. He shall report
to the Publicity Chair. He shall present a record of ticket sales
to the Treasurer.


\subsubsection{Social Chair}

The Social Chair shall oversee all issues relating to the social life
and atmosphere of CMAC. This includes, but is not limited to, the
maintenance and development of CMAC traditions, the planning and execution
of social events, and the regulation of the social atmosphere of CMAC.
He shall report to the Development Chair.


\subsubsection{Philanthropy Chair}

The Philanthropy Chair shall coordinate all philanthropic and charity
efforts of CMAC. This includes, but is not limited to, concerts for
charity, community service days, food and clothing drives, and charitable
donations. He shall report to the Development Chair.


\subsubsection{Music Chair}

The Music Chair shall collaborate closely with the Conductor in maintaining
and developing the musical integrity of CMAC. This includes, but is
not limited to, aiding the President in running rehearsal, conducting
the group in the absence of the Conductor and coordinating Sectionals
with Sectional Leaders. In all musical matters he shall defer to the
judgment of the Conductor. He shall report to the Conductor.


\subsubsection{Newsletter Chair}

The Newsletter Chair shall be responsible for the creation and publishing
of an annual CMAC newsletter. He shall report to the Development Chair.


\subsubsection{Webmaster}

The Webmaster shall be responsible for all oversight regarding CMAC's
domain, www.cmacsings.com, and other web presence. He shall report to the
Publicity Chair.


\subsubsection{Librarian}

The Librarian shall be responsible for maintaining the CMAC catalogue
of music. This includes, but is not limited to, copying and handing
out all new music, and maintaining the records of all old music. He
shall report to the Conductor.


\subsubsection{Special Event Chair}

The Special Event Chair shall be responsible for coordinating all
details related to a specific upcoming special event. The Executive
Board shall enumerate the specific duties of this position based on
the nature of the special event.


\subsubsection{Design Chair}

The Design Chair shall be responsible for designing advertising materials,
including but not limited to posters, invitations, and tickets. He
shall report to the Publicity Chair.

% ** Appointment of the Executive Cabinet
\subsection{Appointment of Executive Cabinet}

With the exception of the Special Events Chair, the Executive Board
shall appoint all Cabinet Members following the Annual Meeting of
CMAC. The Executive Board shall announce cabinet positions no later
than two weeks prior to when appointments are made. Members who are
interested in an Executive Cabinet position are encouraged to make
their desire known to the Executive Board a week before appointments
are made.

% *** Appointment of the Special Event Chair
\subsubsection{Appointment of the Special Event Chair}

The Executive Board shall appoint a Special Event Chair when appropriate.

% *** Appointment of Music Chair
\subsubsection{Appointment of Music Chair}

The Executive Board shall consult with the Conductor when appointing
the Music Chair.

% *** Subsumed Positions
\subsubsection{Subsumed Positions}

In the event of absence of qualified or interested members for a given
Cabinet Position, the duties of the position shall be subsumed by
the Executive Board.

% * Section Leaders
\section{Section Leaders}

% ** Election of Section Leaders
\subsection{Election of Section Leaders}

The Members shall hold elections for section leaders by the fifth
regularly scheduled rehearsal of the year. The Section Leaders shall
be elected, respectively, by the Members of each Section for a term
of one year. Section Leaders must have been Active Members for at
least one academic quarter. Officers are eligible for Section Leader,
but the Membership is encouraged to elect non-Officer Members.

% ** Emergency Election
\subsection{Emergency Election}

In the case of a vacancy occurring more than one month before the
expiration of the term of a Section Leader, the Members of that Section
shall fill such vacancy by special election held as soon as possible
after the vacancy occurs; any Section Leader so elected shall qualify
immediately upon election and shall hold office for the remainder
of the unexpired term.

% ** Duties of Section Leaders
\subsection{Duties of Section Leaders}

Section Leaders shall be the musical leaders of their respective Sections,
and shall:
\begin{enumerate}
\item be the musical and social leaders of their respective section;
\item be responsible for assisting the Conductor in achieving the musical
excellence of the group;
\item maintain clear and accurate records of music rehearsed and musical
notations given during Rehearsals;
\item communicate the same to absent Members of their Sections and otherwise
assist them musically;
\item assist the Secretary in the maintenance of attendance records, the
taking of active steps to discourage absences, and the dissemination
of information to the Members;
\item have the authority to call meetings of their respective sections for
extra practice and to chair or to appoint a chair for said meetings;
\item be responsible for the maintenance and development of traditions for
their section;
\item coordinate with the Social Chair to plan and execute social events
for their section;
\item coordinate with other Section Leaders and with the Social Chair to
plan and execute competitive activities between sections; and
\item he shall attend the first Executive Board meeting after his election,
as well as two more Executive Board meetings in the same quarter,
and two in each of the following quarters.
\end{enumerate}

% ** Presidential Chair of Section Meetings
\subsection{Presidential Chair of Section Meetings}

At his discretion, the President shall chair (or appoint a chairman
for) any meeting of Members of a Section that the Section Leader cannot
or should not chair.

% ** Succession of Section Leaders
\subsection{Succession of Section Leaders}

If a Section Leader is for any reason unable to serve, there shall
be an immediate vote held by the section to nominate a successor and
replace the Section Leader.

% * Conductor
\section{Conductor}

CMAC shall have a Conductor responsible for running all rehearsals
and performances. He shall be appointed by the Board of Directors
and shall have a contract created or renewed each year by them, regarding
expectations for his role and possible compensation for his activities.
He shall not be a member of the Executive Board and shall have no
vote, but he shall always have the right to attend their meetings
and express his opinions therein.

% * Finances
\section{Finances}

% ** Signator
\subsection{Signator}

The Treasurer shall be designated signator of the CMAC Checking Account
and all other Operating Accounts of the group. Any and all purchases
and/or expenditure from this account shall be made only with the consent
of the Board. The Chairman of the Board shall be the signator of the
Alumni Account along with the Treasurer.

% ** Assessment
\subsection{Assessment}

The Treasurer, with the consent of the Board, shall have the authority
to prescribe reasonable assessments of the Active Membership including
trip expenses and other necessary items. These assessments shall be
collected by the Treasurer or designee.

% ** Dues Request
\subsection{Dues Request}

The Treasurer shall submit to the Board an amount to request from
the Membership in member dues. Upon approval of the Board, the Treasurer
or designee shall collect these dues.

% ** Appeal of Assessments
\subsection{Appeal of Assessments}

Any Member may appeal any financial obligations to the Board within
two weeks of the assessment. The Board may decide to delay, reduce,
or cancel any financial obligation.

% ** Revenues
\subsection{Revenues}

The Ticket Czar shall oversee the distribution and sale of concert
tickets and shall transfer all monies raised to the Treasurer. The
Development Chair shall be responsible for the distribution and sale
of recordings or other merchandise. All sales shall be made at a price
determined by the Executive Board.

% ** Fundraising
\subsection{Fundraising}

The Development Chair shall have the authority to raise funds for
CMAC through any and all available means, upon such approval by the
Board of Directors. The Development Chair shall coordinate the contact
of Alumni in order to solicit contributions to the CMAC Operating
Accounts a minimum of once per academic year. He shall delegate these
responsibilities as needed.

% ** CMAC Alumni Accounts and Endowment
\subsection{CMAC Alumni Accounts and Endowment}

The Treasurer shall make regular reports on the status of CMAC's Capital
Campaigns and Endowment accounts to the Board, and shall be responsible
for making requests to CMAC's Alumni Accounts for expenditures from
them. Any and all requests for expenditures of these accounts by the
Treasurer must be approved by the Board.

% ** Financial Transparency
\subsection{Financial Transparency}

By the fifth rehearsal of each quarter, the treasurer shall be responsible
for presenting to the membership the status of CMAC's treasury, including
but not limited to: concert revenues, current balance, and projected
cashflow.

% * Indemnification
\section{Indemnification}

To the fullest extent now or hereafter permitted by the laws of Illinois,
CMAC shall indemnify any person who is or was an Officer against expenses
and liabilities in connection with any proceeding involving such Officer
by reason of his having been in such a position.

% * Ratification and Amendment
\section{Ratification and Amendment}
\begin{enumerate}
\item These Bylaws shall be ratified by a two-thirds majority of the members
and shall become effective immediately thereafter.
\item All amendments or additions to these Bylaws shall be ratified by a
two-thirds majority of the Members present, a quorum requiring three-fourths
of the Active Members.
\end{enumerate}

% * Discrimination
\section{Discrimination}

CMAC considers students on the basis of individual
merit and without regard to race, color, religion, sex, gender, sexual
orientation, national or ethnic origin, age, disability, or other
factors irrelevant to participation in CMAC. However,
CMAC may make requirements based on vocal range or quality that may
result in the group's being composed entirely of one
sex. The University of Chicago has other all-female a cappella groups
which provide a substantially equal single-sex environment for female
students.
\end{document}
